Active Damping of Rotating Positioning Platforms

### 2020-06-24 paper/paper.tex
Add captions

% Created 2020-06-24 mer. 15:36
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\hypersetup{
 pdfauthor={},
 pdftitle={Active Damping of Rotating Positioning Platforms},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 27.0.91 (Org mode 9.4)}, 
 pdflang={English}}
\begin{document}

@@

\section{Introduction}
\label{sec:orgbec19fa}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:org81be86a}
\subsection{Studied Rotating Positioning Platform}
\label{sec:orgf8fad9b}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system.pdf}
\caption{\label{fig:system}Figure caption}
\end{figure}

\subsection{Equation of Motion}
\label{sec:org926ba54}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:org298e237}

@@

\subsection{Constant Rotating Speed}
\label{sec:org8d2eda6}
To simplify, let's consider a constant rotating speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\caption{\label{fig:campbell_diagram}Campbell Diagram}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
\end{subfigure}
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
\end{subfigure}
\caption{\label{fig:plant_compare_rotating_speed}Dynamics}
\centering
\end{figure}

\section{Integral Force Feedback}
\label{sec:org2e8c85f}
\subsection{Control Schematic}
\label{sec:org50b6359}

@@

\subsection{Equations}
\label{sec:org99c13a7}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:org1e476e3}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
\caption{\label{fig:plant_iff_compare_rotating_speed}Figure caption}
\end{figure}

\subsection{Integral Force Feedback}
\label{sec:orga5d8887}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus}
\end{figure}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org569b7db}
\subsection{Modification of the Control Low}
\label{sec:org4d0c1ca}

\subsection{Feedback Analysis}
\label{sec:org1f34d25}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
\caption{\label{fig:loop_gain_modified_iff}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
\caption{\label{fig:root_locus_modified_iff}Figure caption}
\end{figure}

\subsection{Optimal Cut-Off Frequency}
\label{sec:org04a5aa4}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
\caption{\label{fig:mod_iff_damping_wi}Figure caption}
\end{figure}

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org03c54a4}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:orgc2d9221}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}Figure caption}
\end{figure}

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:org8097ba5}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
\caption{\label{fig:plant_iff_kp}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Figure caption}
\end{figure}

\subsection{Optimal Parallel Stiffness}
\label{sec:org1f2e167}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps}Figure caption}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_opt_gain_iff_kp.pdf}
\caption{\label{fig:root_locus_opt_gain_iff_kp}Figure caption}
\end{figure}

\section{Direct Velocity Feedback}
\label{sec:orgda2e325}
\subsection{Control Schematic}
\label{sec:org0e84009}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_dvf.pdf}
\caption{\label{fig:system_dvf}Figure caption}
\end{figure}

\subsection{Equations}
\label{sec:org7cc244c}

\subsection{Relative Direct Velocity Feedback}
\label{sec:org668d842}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_dvf.pdf}
\caption{\label{fig:root_locus_dvf}Figure caption}
\end{figure}

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:orgade0126}
**

**

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_root_locus.pdf}
\caption{\label{fig:comp_root_locus}Figure caption}
\end{figure}

\subsection{Transmissibility and Compliance}
\label{sec:org59b0db2}

@@

\section{Conclusion}
\label{sec:org4b70853}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:org7708a14}

>>>>

% Created 2020-06-24 mer. 16:28
% Intended LaTeX compiler: pdflatex
\documentclass{ISMA_USD2020}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{grffile}
\usepackage{longtable}
\usepackage{wrapfig}
\usepackage{rotating}
\usepackage[normalem]{ulem}
\usepackage{amsmath}
\usepackage{textcomp}
\usepackage{amssymb}
\usepackage{capt-of}
\usepackage{hyperref}
\usepackage[most]{tcolorbox}
\usepackage{bm}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{array}
\usepackage{siunitx}
\usepackage{amsmath,amssymb,amsfonts, cases}
\usepackage{algorithmic, graphicx, textcomp}
\usepackage{xcolor, import, hyperref}
\usepackage{subcaption}
\usepackage[USenglish, english]{babel}
\setcounter{footnote}{1}
\input{config.tex}
\author[1,3] {T. Dehaeze}
\author[1,2] {C. Collette}
\affil[1] {Precision Mechatronics Laboratory\NewLineAffil University of Liege, Belgium \NewAffil}
\affil[2] {BEAMS Department\NewLineAffil Free University of Brussels, Belgium \NewAffil}
\affil[3] {European Synchrotron Radiation Facility \NewLineAffil Grenoble, France e-mail: \textbf{thomas.dehaeze@esrf.fr}}
\bibliographystyle{IEEEtran}
\usepackage{tikz}
\usetikzlibrary{shapes.misc}
\date{}
\title{Active Damping of Rotating Positioning Platforms}
\begin{document}

@@

\section{Introduction}
\label{sec:org3cbd2ff}
\label{sec:introduction}
Controller Poles are shown by black crosses (
\begin{tikzpicture} \node[cross out, draw=black, minimum size=1ex, line width=2pt, inner sep=0pt, outer sep=0pt] at (0, 0){}; \end{tikzpicture}
).
This paper has been published
The Matlab code that was use to obtain the results are available in \cite{dehaeze20_activ_dampin_rotat_posit_platf}.

\section{Dynamics of Rotating Positioning Platforms}
\label{sec:org3cf58d1}
\subsection{Studied Rotating Positioning Platform}
\label{sec:orgf321431}
Consider the rotating X-Y stage of Figure \ref{fig:system}.

@@

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system.pdf}
\caption{\label{fig:system}Schematic of the studied System}
\end{figure}

\subsection{Equation of Motion}
\label{sec:org9612ace}
The system has two degrees of freedom and is thus fully described by the generalized coordinates \(u\) and \(v\) (describing the position of the mass in the rotating frame).

@@

\subsection{Transfer Functions in the Laplace domain}
\label{sec:org1590670}

@@

\subsection{Constant Rotational Speed}
\label{sec:orgd9375df}
To simplify, let's consider a constant rotational speed \(\dot{\theta} = \Omega\) and thus \(\ddot{\theta} = 0\).

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_real.pdf}
\caption{\label{fig:campbell_diagram_real} Real Part}
\end{subfigure}
\begin{subfigure}[c]{0.4\linewidth}
\includegraphics[width=\linewidth]{figs/campbell_diagram_imag.pdf}
\caption{\label{fig:campbell_diagram_imag} Imaginary Part}
\end{subfigure}
\caption{\label{fig:campbell_diagram}Campbell Diagram : Evolution of the poles as a function of the rotational speed \(\Omega\)}
\centering
\end{figure}

@@

\begin{figure}[htbp]
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_direct.pdf}
\caption{\label{fig:plant_compare_rotating_speed_direct} Direct Terms \(d_u/F_u\), \(d_v/F_v\)}
\end{subfigure}
\begin{subfigure}[c]{0.45\linewidth}
\includegraphics[width=\linewidth]{figs/plant_compare_rotating_speed_coupling.pdf}
\caption{\label{fig:plant_compare_rotating_speed_coupling} Coupling Terms \(d_v/F_u\), \(d_u/F_v\)}
\end{subfigure}
\caption{\label{fig:plant_compare_rotating_speed}Bode Plots for \(\bm{G}_d\)}
\centering
\end{figure}

\section{Integral Force Feedback}
\label{sec:org95f47e8}
\subsection{Control Schematic}
\label{sec:org8bb26ea}

@@

\subsection{Equations}
\label{sec:orgbd9ebe0}
The sensed forces are equal to:
\begin{equation}
\begin{bmatrix} f_{u} \\ f_{v} \end{bmatrix} =
\begin{bmatrix} F_u \\ F_v \end{bmatrix} - (c s + k)
\begin{bmatrix} d_u \\ d_v \end{bmatrix}
\end{equation}

@@

\subsection{Plant Dynamics}
\label{sec:org392809f}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_compare_rotating_speed.pdf}
\caption{\label{fig:plant_iff_compare_rotating_speed}Bode plot of \(\bm{G}_f\) for several rotational speeds \(\Omega\)}
\end{figure}

\subsection{Integral Force Feedback}
\label{sec:org049877c}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_pure_iff.pdf}
\caption{\label{fig:root_locus_pure_iff}Root Locus for the Decentralized Integral Force Feedback}
\end{figure}

@@

\section{Integral Force Feedback with High Pass Filters}
\label{sec:org54452db}
\subsection{Modification of the Control Low}
\label{sec:org325cdd4}

\subsection{Feedback Analysis}
\label{sec:org5efee77}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/loop_gain_modified_iff.pdf}
\caption{\label{fig:loop_gain_modified_iff}Bode Plot of the Loop Gain for IFF with and without the HPF}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_modified_iff.pdf}
\caption{\label{fig:root_locus_modified_iff}Root Locus for IFF with and without the HPF}
\end{figure}

\subsection{Optimal Cut-Off Frequency}
\label{sec:orgd5828e4}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_wi_modified_iff.pdf}
\caption{\label{fig:root_locus_wi_modified_iff}Root Locus for several HPF cut-off frequencies \(\omega_i\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/mod_iff_damping_wi.pdf}
\caption{\label{fig:mod_iff_damping_wi}Attainable damping ratio \(\xi_\text{cl}\) as a function of the HPF cut-off frequency. Corresponding control gain \(g_\text{opt}\) and \(g_\text{max}\) are also shown}
\end{figure}

\section{Integral Force Feedback with Parallel Springs}
\label{sec:org22884d6}
\subsection{Stiffness in Parallel with the Force Sensor}
\label{sec:orgb871bfd}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_parallel_springs.pdf}
\caption{\label{fig:system_parallel_springs}System with added springs \(k_p\) in parallel with the actuators}
\end{figure}

\subsection{Effect of the Parallel Stiffness on the Plant Dynamics}
\label{sec:org4d37cce}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/plant_iff_kp.pdf}
\caption{\label{fig:plant_iff_kp}Bode Plot of \(f_u/F_u\) without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kp.pdf}
\caption{\label{fig:root_locus_iff_kp}Root Locus for IFF without any parallel stiffness, with a parallel stiffness \(k_p < m \Omega^2\) and with \(k_p > m \Omega^2\)}
\end{figure}

\subsection{Optimal Parallel Stiffness}
\label{sec:orgd19b212}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_iff_kps.pdf}
\caption{\label{fig:root_locus_iff_kps}Root Locus for IFF for several parallel spring stiffnesses \(k_p\)}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_opt_gain_iff_kp.pdf}
\caption{\label{fig:root_locus_opt_gain_iff_kp}Root Locus for IFF with \(k_p = 5 m \Omega^2\). The poles of the system using the gain that yields the maximum damping ratio are shown by black crosses}
\end{figure}

\section{Direct Velocity Feedback}
\label{sec:org6904969}
\subsection{Control Schematic}
\label{sec:org103e18b}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/system_dvf.pdf}
\caption{\label{fig:system_dvf}System with relative velocity sensors and with decentralized controllers \(K_V\)}
\end{figure}

\subsection{Equations}
\label{sec:org793c22d}

\subsection{Relative Direct Velocity Feedback}
\label{sec:orgc28d518}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/root_locus_dvf.pdf}
\caption{\label{fig:root_locus_dvf}Root Locus for Decentralized Direct Velocity Feedback for several rotational speeds \(\Omega\)}
\end{figure}

\section{Comparison of the Proposed Active Damping Techniques for Rotating Positioning Stages}
\label{sec:org6af1fdb}
\subsection{Physical Comparison}
\label{sec:orgdff3aa2}

\subsection{Attainable Damping}
\label{sec:org22c8f42}

\begin{figure}[htbp]
\centering
\includegraphics[scale=1]{figs/comp_root_locus.pdf}
\caption{\label{fig:comp_root_locus}Root Locus for the three proposed decentralized active damping techniques: IFF with HFP, IFF with parallel springs, and relative DVF}
\end{figure}

\subsection{Transmissibility and Compliance}
\label{sec:org3e2cf56}

@@

\section{Conclusion}
\label{sec:orge292803}
\label{sec:conclusion}

\section*{Acknowledgment}
\label{sec:orgaf681fb}
